\documentclass[10pt, ]{article}

\usepackage[utf8]{inputenc}
\usepackage[a4paper, top = 2cm, left = 2cm, bottom = 2cm, right = 2cm]{geometry} 
\usepackage{hyperref}
\usepackage[anythingbreaks]{breakurl}
\usepackage{mathtools, amsthm, amssymb, amsbsy}
\usepackage[shortlabels]{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{ragged2e}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{changepage}

\usepackage[T1]{fontenc}
\usepackage{lmodern}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\rhead{\thepage\,of \pageref{LastPage}}
\rfoot{{\scriptsize Last updated on \today.}}

\linespread{1.25} 
% \pagenumbering{gobble} % Suppress page numbering

\begin{document}
	
	\begin{center}
		{\LARGE André Victor Ribeiro Amaral} \\ \vspace{3pt}
		% {\small DOB: March 23, 1994} \\ \vspace{3pt}
		{\small\faEnvelope~~\href{mailto:avramaral@gmail.com}{\texttt{avramaral@gmail.com~~}}} \\
		{\small\faDesktop~~\href{https://www.avramaral.com/}{\texttt{www.avramaral.com/~~~}}}	\\
		{\small\faGithubAlt~~\href{https://github.com/avramaral/}{\texttt{github.com/avramaral/}}}	
	\end{center}
	
	\vspace{-12pt}
	\section*{Research Appointments} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{Post-doctoral Researcher Associate in Mathematics} at \textit{Imperial College London}. London, England. From 01/2024 to CURRENT. \vspace{3pt}
		
		In collaboration with \href{https://www.imperial.ac.uk/people/oliver.ratmann05}{Dr. Oliver Ratmann} and \href{https://www.imperial.ac.uk/people/adam.sykulski}{Dr. Adam Sykulski}, I work on the development of novel, flexible and computationally tractable spatio-temporal statistical inference tools and on their application in the domains of (1) species mapping and forecasting utilizing oceanographic and climatological data, and (2) quantification and hotspot mapping of orphanhood levels worldwide.
		
	\end{enumerate}
	
	% \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}
	
	\vspace{-12pt}
	\section*{Education} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{Ph.D. in Statistics}, King Abdullah University of Science and Technology (KAUST). Thuwal, Saudi Arabia. From 08/2020 to 12/2023. Advised by \href{https://www.paulamoraga.com/}{Dr. Paula Moraga}. % GPA: 3.62 (out of 4).
		\\
		Dissertation title: \textit{Spatial and Spatio-temporal Statistical Methods for Environment and Public Health Applications}. \href{https://repository.kaust.edu.sa/handle/10754/695717}{\url{https://repository.kaust.edu.sa/handle/10754/695717}}.
		
		\item \textbf{M.S. in Statistics}, Universidade Federal de Minas Gerais (UFMG). Belo Horizonte, Brazil. From 02/2019 to 06/2020. Advised by \href{http://www.est.ufmg.br/~rogerwcs/}{Dr. Roger Silva}. % GPA: 84.5 (out of 100). 
		\\
		Dissertation title: \textit{Phase Transition Phenomenon in Percolation Models using Boolean Functions} (written in Portuguese). \href{http://hdl.handle.net/1843/51318}{\url{http://hdl.handle.net/1843/51318}}.
		
		%\item \textbf{B.S. in Statistics}, Universidade Federal de Minas Gerais (UFMG). Belo Horizonte, Brazil. From 02/2018 to 12/2018 (Interrupted due to the admission into the Master's Program).
		
		%\item \textbf{B.S. in Industrial Engineering}, Pontifícia Universidade Católica de Minas Gerais (PUC Minas). Belo Horizonte, Brazil. From 02/2012 to 06/2018 \hspace{-1pt}(Completed). %GPA: 85.58 \hspace{-1pt}(out of 100).
		
	\end{enumerate}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}
	
	\vspace{-12pt}
	\section*{Publications} \vspace{-5pt}
	
	\begin{itemize}[noitemsep, topsep=0pt]
		\item[$\circ$]  \textbf{Peer-reviewed}
		\begin{enumerate}[label*=\arabic*., noitemsep]
		\item  \textbf{Amaral, AVR}, Rubio, FJ, Quaresma, M, Rodríguez-Cortés, FJ, and Moraga, P (2024). \textit{Extended Excess Hazard Models for Spatially Dependent Survival Data}. Statistical Methods in Medical Research (SMMR). \href{https://doi.org/10.1177/09622802241233767}{\url{https://doi.org/10.1177/09622802241233767}}.
		\item  \textbf{Amaral, AVR}, Krainski, ET, Zhong, R, and Moraga, P (2023). \textit{Model-based Geostatistics under Spatially Varying Preferential Sampling}.  Journal of Agricultural, Biological and Environmental Statistics. \url{https://doi.org/10.1007/s13253-023-00571-0}.
		\item  \textbf{Amaral, AVR}, González, JA, and Moraga, P (2022). \textit{Spatio-temporal modeling of infectious diseases by integrating compartment and point process models}. Stochastic Environmental Research and Risk Assessment. \url{https://doi.org/10.1007/s00477-022-02354-4}.
		\item  Mahmood, M, \textbf{Amaral, AVR}, Mateu, J, and Moraga, P (2022). \textit{Modeling infectious disease dynamics: Integrating contact tracing-based stochastic compartment and spatio-temporal risk models}. Spatial Statistics. \url{https://doi.org/10.1016/j.spasta.2022.100691}.
		\end{enumerate}
		\item[$\circ$] \textbf{Preprint}
		\begin{enumerate}[label*=\arabic*., noitemsep]
			\item  Zhong, R, \textbf{Amaral, AVR}, and Moraga, P (2024).\textit{ Spatial data fusion adjusting for preferential sampling using INLA and SPDE}. arXiv preprint. \href{https://arxiv.org/abs/2309.03316}{\url{https://arxiv.org/abs/2309.03316}}. Accepted in Journal of the Royal Statistical Society (Series A).
		\end{enumerate}
		\item[$\circ$] \textbf{Others}
		\begin{enumerate}[label*=\arabic*., noitemsep]
			\item \textbf{Amaral, AVR}, Wolffram, D, Moraga, P, and Bracher, J (2024+). \textit{The nowcast puzzle: post-processing and weighted combination of infectious disease nowcasts}. In preparation.
		\end{enumerate}
	\end{itemize}
	\vspace{-2pt}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}
	
	\vspace{-12pt}
	\section*{Teaching} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{Mini-course Instructor} in ``Machine Learning \& Global Health (MLGH) Workshop at Imperial College London.'' 04/2024. The material (INLA Tutorial) is available on  \href{https://avramaral.github.io/INLA_tutorial/}{\url{https://avramaral.github.io/INLA_tutorial/}}.
		
		\item \textbf{Guest lecturer} in ``Spatial Statistics'' (MATH60139/70139), Imperial College London. Spring, 2024. Invited by \href{https://www.imperial.ac.uk/people/adam.sykulski}{Dr. Adam Sykulski}. The material (Inference on Point Processes) is available on \href{https://avramaral.github.io/PP_inference/}{\url{https://avramaral.github.io/PP_inference/}}.
		
		\item \textbf{Mini-course Instructor} in the ``Spatio-temporal Point Pattern Data Analysis with Applications in Health Surveillance and Environmental Data'' course, taught during the ``International Conference on Bioinformatics (InCoB2022).'' 11/2022. The material is available on  \href{https://avramaral.github.io/PP_tutorial/}{\url{https://avramaral.github.io/PP_tutorial/}}.
		
		\item \textbf{Graduate Teaching Assistant} in ``Applied Statistics with R'' (STAT 215), King Abdullah University of Science and Technology. Twice (Fall, 2021 and 2022). Advised by \href{https://cemse.kaust.edu.sa/people/person/joaquin-ortega-sanchez}{Dr. Joaquin Ortega}. The material is available on \href{https://avramaral.github.io/STAT215/}{\url{https://avramaral.github.io/STAT215/}}.
		
		\item \textbf{Teaching Assistant} in ``Applied Statistics and Data Analysis'' (DSA004). This was a four-day course given to ARAMCO employees in collaboration with King Abdullah University of Science and Technology. Summer, 2022. Advised by \href{https://www.paulamoraga.com/}{Dr. Paula Moraga}. The material is available on \href{https://avramaral.github.io/aramco\_course/}{\url{https://avramaral.github.io/aramco\_course/}}.
		
		\item \textbf{Graduate Teaching Assistant} in ``Contemporary Topics in Statistics'' (STAT 294), King Abdullah University of Science and Technology. Fall, 2021. Advised by \href{https://www.paulamoraga.com/}{Dr. Paula Moraga}. The material is available on \href{https://avramaral.github.io/STAT294/}{\url{https://avramaral.github.io/STAT294/}}.
		
		\item \textbf{Graduate Teaching Assistant} in ``Statistics and Probability'' (EST 031), Universidade Federal de Minas Gerais. From 02/2020 to 06/2020. Advised by \href{http://www.est.ufmg.br/~cristianocs/}{Dr. Cristiano Carvalho}. The material (written in Portuguese) is available on \href{https://avramaral.github.io/AulasEstProb/}{\url{avramaral.github.io/AulasEstProb/}}.
	\end{enumerate}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}
	
	\vspace{-12pt}
	\section*{Conference Presentations} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{Talk} at ``CEN 2023.'' 09/2023. \textit{Extended Excess Hazard Models for Spatially Dependent Survival Data}. The slides are available on \href{https://github.com/avramaral/AC/tree/main/CEN\_2023}{\url{https://github.com/avramaral/AC/tree/main/CEN\_2023}}.
		
		\item \textbf{Talk} at ``JSM 2023.'' 08/2023. \textit{Model-based Geostatistics under Spatially Varying Preferential Sampling}. The slides are available on \href{https://github.com/avramaral/AC/tree/main/JSM\_2023}{\url{https://github.com/avramaral/AC/tree/main/JSM\_2023}}.
		
		\item \textbf{Poster presentation} at ``KAUST 2022 Workshop on Statistics.'' 11/2022. \textit{Extended Excess Hazard Model for Spatially Dependent Survival Data with Applications to Cancer Research}. The poster is available on \href{https://github.com/avramaral/AC/tree/main/KAUST_2022_STAT_WORKSHOP}{\url{https://github.com/avramaral/AC/tree/main/KAUST_2022_STAT_WORKSHOP}}.
		
		\item \textbf{Talk} and \textbf{poster presentation} at ``JSM 2022.'' 08/2022. \textit{Integrating Compartment and Point Process Models for Spatio-Temporal Modeling of Infectious Diseases}. The slides and poster are available on \href{https://github.com/avramaral/AC/tree/main/JSM\_2022}{\url{https://github.com/avramaral/AC/tree/main/JSM\_2022}}.
		
		\item \textbf{Talk} at ``GeoEnv 2022.'' 06/2022. \textit{Spatio-temporal Point Process Compartment Modeling for Infectious Diseases}. The slides are available on \href{https://github.com/avramaral/AC/tree/main/GeoEnv\_2022}{\url{https://github.com/avramaral/AC/tree/main/GeoEnv\_2022}}.
		
		\item \textbf{Poster presentation} at ``METMA X.'' 06/2022. \textit{Assessing the Effect of Model-based Geostatistics Under Preferential Sampling for Spatial Data Analysis}. The poster is available on \href{https://github.com/avramaral/AC/tree/main/METMA\_X}{\url{https://github.com/avramaral/AC/tree/main/METMA\_X}}.
		
		\item \textbf{Talk} at ``ENAR 2022.'' 03/2022. \textit{Modeling Infectious Disease Dynamics: Integrating Contact Tracing-based	Stochastic Compartment and Spatio-temporal Risk Models}. The slides are available on \href{https://github.com/avramaral/AC/tree/main/ENAR\_2022}{\url{https://github.com/avramaral/AC/tree/main/ENAR\_2022}}.
		
		\item \textbf{Poster presentation} at ``TWAS 15${}^{\text{th}}$ General Conference.'' 11/2021. \textit{Modeling Infectious Disease Dynamics: Integrating Contact Tracing-based	Stochastic Compartment and Spatio-temporal Risk Models}. The poster is available on \href{https://github.com/avramaral/AC/tree/main/TWAS\_15}{\url{https://github.com/avramaral/AC/tree/main/TWAS\_15}}.
	\end{enumerate}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}

	\vspace{-12pt}
	\section*{Grants} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{FoNS Researcher Mobility Grant for Postdocs and Fellows} (Imperial College London): Travel grant for a 3-week research visit to the Inria Centre at Université de Lorraine (in France). \hspace{-1pt}05/2024. \hspace{-1pt}£2,000.
		
		\item \textbf{KHYS Aspirant Grant} (Karlsruhe Institute of Technology): Travel grant for a 30-day research visit to the Karlsruhe Institute of Technology (in Germany). 09/2023. €1,200.
	\end{enumerate}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}
	
	\vspace{-12pt}
	\section*{Honors and Awards} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{CEMSE Dean's List Award}, by King Abdullah University of Science and Technology. Academic years 2021/2022 and 2022/2023.
		
		\item \textbf{Graduate Fellowship}, by King Abdullah University of Science and Technology (KAUST). From 08/2020 to 12/2023. \vspace{3pt}
		
		The Fellowship is a competitive grant awarded to graduate students at KAUST. The grant consisted of direct research costs and living expenses. Under the supervision of \href{https://www.paulamoraga.com/}{Dr. Paula Moraga}, I  worked on the development of statistical methods for geospatial data analysis with applications in health surveillance. \vspace{3pt}
		
		\item \textbf{Undergraduate Scholarship}, by Brazil's ``Science without Borders'' Program. From 07/2016 to 12/2017.\vspace{3pt}
		
		The Scholarship was granted to excellent students from Brazil who wanted to complete part of their undergraduate education in other Educational Institutions overseas. It covered tuition and living expenses. I completed the program as a student at Curtin University (in Australia).
		
	\end{enumerate}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}
	
	\vspace{-12pt}
	\section*{Participation and Attendance} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item Eight-week visiting period at the Karlsruhe Institute of Technology (in Germany) under the supervision of \href{https://jbracher.github.io/}{Dr. Johannes Bracher}. 05/2023 and 09/2023.\vspace{3pt}
		
		We worked in the development of a framework for post-processing and combining \textit{nowcasting} models, and applied it to ``COVID-19 7-day hospitalization incidence'' in Germany.\vspace{3pt}
		
		\item Summer school: Bayesian methods in health economics (2023).  07/2023.
		
		\item Three-week visiting period at University College London (in the United Kingdom) under the supervision of \href{https://sites.google.com/site/fjavierrubio67/}{Dr. Javier Rubio}. 10/2022.\vspace{3pt}
		
		We worked on the development of a statistical class of models for modeling spatially dependent survival data under the assumption of competing risks and unknown cause-of-death. We applied this methodology to the modeling of the hazard function for patients diagnosed with colon cancer in England.\vspace{3pt}
		
		% we worked on the development of a general class of statistical models (along with inference tools) for survival data analysis. In particular, we modeled the hazard function for cancer-diagnosed patients assuming unknown causes of death (also known as ``relative survival framework'') and spatial autocorrelation.
		
		\item Gaussian Process Modeling, Design, and Optimization. Professional Development Continuing Education Course at ``JSM 2022.'' 08/2022.
		
		\item 13${}^{\text{th}}$ Summer Institute in Statistics and Modeling in Infectious Diseases (SISMID). 07/2021. I attended the following modules \vspace{-6pt}
		\begin{enumerate}[label*=\arabic*., noitemsep]
			\item Module 7: Simulation-Based Inference for Epidemiological Dynamics.
			\item Module 9: Contact Network Epidemiology.
			\item Module 12: Statistics and Modeling with Novel Data Streams.
		\end{enumerate}
		
		\item València International Bayesian Analysis Summer School, 4${}^{\text{th}}$ Edition (VIBASS4). 07/2021.
		
		\item Duke Machine Learning Virtual Summer School 2021. 06/2021.
	\end{enumerate}
	
	%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.5pt}}
	\vspace{10pt}

	\vspace{-12pt}
	\section*{Miscellaneous} \vspace{-5pt}
	
	\begin{enumerate}[noitemsep, topsep=0pt]
		\item \textbf{Student Ambassador} in the\textit{ Computer, Electrical,  and Mathematical Science and Engineering} (CEMSE) division at King Abdullah University of Science and Technology (KAUST). Academic year 2022/2023.
		
		As a representative of the Statistics Program at KAUST, I helped in communicating the program to prospective students and answering their questions.
	\end{enumerate}
	
\end{document}



